Stochastic Approximation Monte Carlo with a Dynamic Update Factor

### 2019-06-25 papers/histogram/sad.tex
sad paper edit and aps figure update script.

Schneider et. al outlines minor refinements to the $1/t$-WL algorithm
including $\nicefrac{N_S}{t}$ scaling and switching from standard WL
to $1/t$-WL when the update factor $\gamma <
\nicefrac{N_S}{t}$~\cite{schneider2017convergence}. As per the
original $1/t$ implementation~\cite{belardinelli2007fast}, the update
factor is decreased once all $N_S$ energy states are visited at least
once (i.e. $H(E) \neq 0$) effectively avoiding the concept of
`flatness'.  In this work, we refer to this refined algorithm as $1/t$-WL,
with the update factor asymptoting to $\nicefrac{N_S}{t}$.

>>>>

Schneider et. al outline minor refinements to the $1/t$-WL algorithm
including $\nicefrac{N_S}{t}$ scaling and switching from standard WL
to $1/t$-WL when the update factor $\gamma <
\nicefrac{N_S}{t}$~\cite{schneider2017convergence}. As per the
original $1/t$ implementation~\cite{belardinelli2007fast}, the update
factor is decreased once all $N_S$ energy states are visited at least
once (i.e. $H(E) \neq 0$) effectively avoiding the concept of
`flatness'.  In this work, we refer to this refined algorithm as $1/t$-WL,
with the update factor asymptoting to $\nicefrac{N_S}{t}$.
